\Large \bf Cyclone: High Availability for Persistent Key Value Stores

### 2017-07-29 paper/paper.tex
Updates to paper.

Cyclone takes a software only approach to improving replication performance
using commodity network hardware. In contrast, Mojim~\cite{mojim} pairs directly
attached persistent memory with RDMA to replicate persistent data structures. A
comparison is hard since Mojim is designed for the hypothetical scenario where
there is enough persistent memory to hold all persistent data, while Cyclone is
designed for the practical case where both the write-ahead log and key value
store data structures need to be maintained largely on flash. Nevertheless we
can compare their replication performance for the case where we use only the NVM
log in Cyclone. On 40Gbps infiniband, Mojim reported being able to mirror data
at 4GB/s. In contrast, Cyclone can replicate data three ways using 4*10 Gbps
commodity ethernet NICs at a peak of roughly 3.7 GB/s. This is with
Cyclone is also running the RAFT consensus protocol, while Mojim is doing simple
mirroring of main memory. One can conclude that network offload via RDMA and
Infiniband is not an a-priori requirement for high throughput replication. This
is made possible by Cyclone's approach that relieves the CPU from the burden of
data copies. Of course, the latency of a hop on commodity ethernet at 5 us with
our DPDK stack is larger than the close to 2us latency with
Infiniband. Depending on the use case for the key value store application the
extra 6us with ethernet for the round trip to the replica might be a concern for
some applications. We note that mapping the commutativity of key value store
interfaces to multiple logs in Cyclone is a technique that can also be applied
to RDMA. Mojim confirms that concurrency is a significant
determinant of performance when replicating over RDMA.

@@

DARE~\cite{dare} implements state machine replication over RDMA, using a custom
replication protocol. It is worthwhile to point out that since DARE allows any
replica to become the leader it requires a log adjustment protocol for the
leader to bring its logs up to date, a situation we avoid by using RAFT as
described in Section~\ref{sec:dm}. Using 40 Gb/s speeds, and 3-way replication
DARE reported being able to replicate 500K requests/sec. This is without
persisting the log of updates. In contrast, Cyclone replicates upwards of 6
million similarly sized requests each second with 4*10 Gbps ethernet (without the
second level flashlog). The conclusions we can draw are similar to the
comparison with Mojim: a carefully implemented log replication system obviates
the need for network offload.

>>>>

Cyclone takes a software only approach to improving replication performance
using commodity network hardware. In contrast, Mojim~\cite{mojim} pairs directly
attached persistent memory with RDMA to replicate persistent data structures. A
comparison is hard since Mojim is designed for the hypothetical scenario where
there is enough persistent memory to hold all persistent data, while Cyclone is
designed for the practical case where both the write-ahead log and key value
store data structures need to be maintained largely on flash. Nevertheless we
can compare their replication performance for the case where we use only the NVM
log in Cyclone. On 40Gbps infiniband, Mojim reported being able to mirror data
at 4GB/s. In contrast, Cyclone can replicate data three ways using 4*10 Gbps
commodity ethernet NICs at a peak of roughly 3.7 GB/s. This is with
Cyclone is also running the RAFT consensus protocol, while Mojim is doing simple
mirroring of main memory. One can conclude that network offload via RDMA and
Infiniband is not an a-priori requirement for high throughput replication. This
is made possible by Cyclone's approach that relieves the CPU from the burden of
data copies. On the other hand, the latency of a hop on commodity ethernet at 5 us with
our DPDK stack is larger than the close to 2us latency with
Infiniband. Depending on the use case for the key value store application the
extra 6us with ethernet for the round trip to the replica might be a concern for
some applications. We note that mapping the commutativity of key value store
interfaces to multiple logs in Cyclone is a technique that can also be applied
to RDMA. Mojim confirms that concurrency is a significant
determinant of performance when replicating over RDMA.

@@

DARE~\cite{dare} implements state machine replication over RDMA, using a custom
replication protocol. DARE does not consider persistence in its design. It is
worthwhile to point out that since DARE allows any replica to become the leader
it requires a log adjustment protocol for the leader to bring its logs up to
date, a situation we avoid by using RAFT as described in
Section~\ref{sec:dm}. Using 40 Gb/s speeds, and 3-way replication DARE reported
being able to replicate 500K requests/sec. This is without persisting the log of
updates. In contrast, Cyclone replicates upwards of 6 million similarly sized
requests each second with 4*10 Gbps ethernet (without the second level
flashlog). DARE reports an unloaded write latency of 15us, which is lower than
the unloaded write latency of Cyclone at 20us, thanks to infiniband. The
conclusions we can draw are similar to the comparison with Mojim: a carefully
implemented log replication system obviates the need for network offload when
doing replication.
